### 2014-02-21 paper/retrofit.tex
idiot typo
minor

We consider language of the form |(S, E, e, ->)|, where |S| is some
global state, |E| is an evaluation context, |e| is an expression in
the language and |->| is the reduction relation on the state,
evaluation context and expression;
we say expression |e| in context |E| and state |S| reduces to
expression |e'| in context |E'| and state |S'| and write
|conf S (E[e]) -> conf S' (E'[e'])|.
$|->| : (|S| \times |E| \times |e|) \rightharpoonup (|S| \times |E| \times |e|)$

@@

\begin{mathpar}
\and
\inferrule[T-pure]
{| te ~> te'|}
{| conf tS (iniE te) -> conf tS (iniE te') |}

@@

>>>>

We consider languages in the form of abstract state machines |(tS, tE,
te, ->)|, where |tS| is the global machine state, |tE| is an evaluation
context, |te| is an expression in the language and |->| is the
reduction relation on such configuration, i.e., $|->| : (|tS| \times
|tE| \times |te|) \rightharpoonup (|tS| \times |tE| \times |te|)$

@@

\begin{mathpar}
\and
\inferrule[T-pure]
{| te ~> te'|}
{| conf tS (intE te) -> conf tS (intE te') |}

@@

\subsection{Generalizing further}

\begin{itemize}
\item Label transition systems.
\item Arbitrary scheduling policies $\alpha$
\end{itemize}
